Tables

### 2018-06-27 code/figures.rmd
Changed rs to rp (Replication Project)
Also added simulation data, as RDS files because .csv files were too large

# ggsave("I2_effect_size.png")

@@

# ggsave("H2_effect_size.png")

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
effect_het
# save_plot("effect_het.png", effect_het,
          # nrow = 2, base_aspect_ratio = 1.3)

@@

```{r Plot_tau_against_I2, fig.asp = 0.618}
dat3 <- readRDS("temp_sim_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

@@

```{r Density_plot, fig.asp= 0.618}
dens <- readRDS("temp_sim_results_2.RDS")
names(dens) <-  sort(unique(dat$effect))

#Simulated data at various heterogeneity levels, prep for plotting
I2_dist <- dens %>% 
  bind_rows(.id = "effect") %>% 
  rename(heterogeneity = tau_index) %>% 
  mutate(heterogeneity = recode(heterogeneity,
                            '1' = "Zero",
                            '2' = "Small",
                            '3' = "Medium",
                            '4' = "Large"),
         heterogeneity = as.factor(heterogeneity))

#Observed I2 estimates, i.e, results from main table, see table.rmd
#Effects estimated with sourced function 'est_heterogeen_smd_raw'
observed <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% 
  select(effect, I2 = s_I2) %>%
  mutate(heterogeneity = "Observed")

ggplot(I2_dist, aes(x = I2, group = heterogeneity, fill = heterogeneity, linetype = heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 50, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"), breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
  scale_color_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed"))

>>>>

@@

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
effect_het
# save_plot("../figures/effect_het.png", effect_het,
          # nrow = 2, base_aspect_ratio = 1.3)

@@

```{r Plot_tau_against_I2, fig.asp = 0.618}
dat3 <- readRDS("../data/tau_simulation_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

# ggsave("../figures/tau-I2.png")

@@

```{r Density_plot, fig.asp= 0.618}
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))

#Simulated data at various heterogeneity levels, prep for plotting
I2_dist <- dens %>% 
  bind_rows(.id = "effect") %>% 
  rename(Heterogeneity = tau_index) %>% 
  mutate(Heterogeneity = recode(Heterogeneity,
                            '1' = "Zero",
                            '2' = "Small",
                            '3' = "Medium",
                            '4' = "Large"),
         Heterogeneity = as.factor(Heterogeneity))

#Observed I2 estimates, i.e, results from main table, see table.rmd
#Effects estimated with sourced function 'est_heterogeen_smd_raw'
observed <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% 
  select(effect, I2 = s_I2) %>%
  mutate(Heterogeneity = "Observed")

ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
  geom_density(alpha = 0.3) +
  theme_classic() +
  coord_cartesian(xlim = c(0, 100))  +
  scale_fill_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"), breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
  scale_color_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed"))

# ggsave("../figures/density-I2.png")
```

### 2018-06-27 code/tables.rmd
Changed rs to rp (Replication Project)
Also added simulation data, as RDS files because .csv files were too large

summary.table <- dat %>% 
  group_by(rs) %>% 
  summarize(k = n_distinct(Site),
            Countries = n_distinct(country), 
            Effects = n_distinct(effect),
            Participants = if(Effects == 1){sum(Ntotal)}
                           else{sum(Ntotal) / Effects}) %>% #average across effects
  mutate(Paper = papers) %>% 
  select(RS = rs, Paper, everything()) #change order of columns

summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
  kable_styling() %>% 
  column_spec(2, width = "25em") %>% #specify width of paper column
  footnote(threeparttable = TRUE,
           general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. Participant numbers are those used for primary analyses by original authors (i.e., after exclusions). RS = Replication Study, k = no. primary studies, ML = Many Labs, RRR = Registered Replication Report. (OSF.io/XXXX)")
```

@@

#Add rs and k to the data-frame and prep for table
het <- dat %>% 
  select(rs, Site, effect, effect_type) %>% 
  group_by(rs, effect) %>% 
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD"))

#Load simulation results (power/type 1 error for all effects)
dens <- readRDS("temp_sim_results_2.RDS")
names(dens) <-  sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_ci_lb) %>% 
  select(rs, effect,k , everything()) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound
```

@@

het %>% knitr::kable("latex", align = "c", booktabs = TRUE,  digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 8, "Heterogeneity & error/power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  footnote(threeparttable = TRUE, escape = FALSE,
           general = " Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RS = Replication Study, k = no. primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of I2 95\\\\% confidence interval, ci.ub = upper bound of I2 95\\\\% confidence interval. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. (OSF.io/XXXX)")

>>>>

summary.table <- dat %>% 
  group_by(rp) %>% 
  summarize(k = n_distinct(Site),
            Countries = n_distinct(country), 
            Effects = n_distinct(effect),
            Participants = if(Effects == 1){sum(Ntotal)}
                           else{sum(Ntotal) / Effects}) %>% #average across effects
  mutate(Paper = papers) %>% 
  select(RP = rp, Paper, everything()) #change order of columns

summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
  kable_styling() %>% 
  column_spec(2, width = "25em") %>% #specify width of paper column
  footnote(threeparttable = TRUE,
           general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. Participant numbers are those used for primary analyses by original authors (i.e., after exclusions). RP = Replication Project, k = no. primary studies, ML = Many Labs, RRR = Registered Replication Report. (OSF.io/XXXX)")
```

@@

#Add rp and k to the data-frame and prep for table
het <- dat %>% 
  select(rp, Site, effect, effect_type) %>% 
  group_by(rp, effect) %>% 
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD"))

#Load simulation results (power/type 1 error for all effects)
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

#Combine dataframes to create full table
het <-  het %>% 
  left_join(I2_ci_lb) %>% 
  select(rp, effect,k , everything()) %>% 
  arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound

@@

het %>% knitr::kable("latex", align = "c", booktabs = TRUE,  digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 8, "Heterogeneity & error/power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>%
  footnote(threeparttable = TRUE, escape = FALSE,
           general = " Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, k = no. primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of $I^2$ 95\\\\% confidence interval, ci.ub = upper bound of $I^2$ 95\\\\% confidence interval. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. (OSF.io/XXXX)",
           alphabet = "These effects were simulated as standardized mean differences")
